---
title: "ICT_LIS_661_Final_Project"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem Statement [5 points]

> Describe the data problem(s) you are addressing and what research questions related to the problem(s) you are asking. [3 points]



> Provide some contextual information related to the problem(s). [2 points]



# Data Description, Preparation, and Exploration [10 points]

> In the code chunk below, run all the code necessary to respond to the questions below; please note that this should include at least one visualization! [2 points]

```{r}

```

> Describe your dataset, including a reference, a description of the data collection procedure, and its size (number of observations and variables). [2 points]



> Explain how you imported and manipulated the data for analysis. [2 points]



> Provide the description of key variables and their descriptive statistics. What do these descriptive statistics tell you about the data? [2 points]



> Explain how you visualized the data, why you chose that visualization, and what it tells you about the data. [2 points]



# Hypotheses [5 points]

> In the code chunk below, run all the code necessary to respond to the questions below. Please note that it is not necessary to run any analyses in this part of the project, so you may not need to run any code here. This is here just in case you do!

```{r}

```

> Describe at least four research hypotheses you wish to test, and explain each hypothesis in detail—in terms of the variables identified above. [5 points]



# Analysis Methods [10 points]

> Describe your data analysis methods for testing your hypotheses. [5 points]



> Explain why those data analysis methods are useful for testing your hypotheses. [5 points]



# Results and Discussion [20 points]

> In the code chunk below, run all the code necessary to carry out the analyses described above. [8 points]

```{r}

```


> Interpret the results above. [4 points]



> Discuss any practical implications of your results. [4 points]



> Describe any limitations of your data analyses. [4 points]



# Submitting the Project

After you've completed all parts of this assignment to your satisfaction, click on the `Knit` button in the toolbar at the top of this pane. When/if prompted, please indicate that you wish to knit to an HTML file. Knitting to PDF or Word are fancy tricks but take some more setting up, and that's beyond the scope of this class. 

After RStudio has finished knitting the file, it will bring it up in a special RStudio interface. You can use this interface to review the document and make sure that everything appears as you want. Then, however, you should navigate to the same folder where you have stored this `.Rmd` file, and you will find a `.html` file with the same name in that same folder. You can open that file to view this in your browser; more importantly, this is the file that you should submit to Canvas to complete this assignment.

I cannot accept any submission of your work besides the knit `.html` file! If you are having trouble knitting, please get in touch with me instead of submitting the `.Rmd` file and hoping it will work instead. It won't. I don't have your data, I won't see your output, and I can't grade your work without either of those.

Speaking of having your data, though, it would be nice to have access to all the work you've done in addition to the `.html` file. Please open GitHub desktop, navigate to your repository for this class, *commit* the changes that you've made in completing this project, and *push* those changes to GitHub. I will also ask you to do this if you need any help along the way.