---
title: "ICT_LIS_661_Project_3"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Welcome to Project 4!

Before moving on, please make a copy of this file and rename it in a way that makes a clear distinction between the original file and the file you'll eventually submit.

> Under the headers below, I'll provide you with certain instructions, all of them formatted as blockquotes, like this paragraph is. Underneath each set of blockquoted instructions, you should write a response to any questions I ask and fill out any code chunks as I instruct you. At the very end of this document, I'll provide instructions for *knitting* and submitting the `.Rmd` to Canvas.

## Project 4, Part 1: Your Dataset [6 points]

> For this project, you will need to identify a dataset with at least 100 observations and 5 variables. A dataset with at least 1,000 observations and 10 variables would be even better—but not necessary. This does not need to be a publicly available dataset, but please ensure that you can use the dataset legally and ethically. Store the data somewhere in your GitHub repository for this class.

> It is fine for this to be a dataset that you have used previously in this class; in fact, *Part 1* of this project repeats much of Project 2. There's real value in repeating that experience on new data, but I also won't blame you for saving yourself some time and copying over text and code from Project 2. However, if you are reusing a dataset, you must make sure that the dataset is appropriate for performing t-tests and regressions.

> In the code chunk below, please load the dataset into this document. (Keep in mind that you can—and may need to—install and load packages as part of this or any other code chunk). [1 point]

```{r}

```


> As needed, perform any data cleaning (including "tidying") on the text in the code chunk below. [1 point]

```{r}

```


> In the code chunk below, write code to list the variables included in the dataset. Then, below the code chunk, list and explain 2-5 variables that you expect to explore with t-tests and regressions. [1 point]

```{r}

```






> In the code chunk below, calculate descriptive statistics (including mean, median, variance, and standard deviation) for each of the variables you listed above. Then, below the code chunk, describe what those descriptive statistics tell you about those variables. [3 points]


```{r}

```



## Project 3, Part 2: T-Test [6 points]

> For this part of the project, you will be carrying out a t-test. Please recall that the purpose of a t-test is to compare two means!

### Hypotheses

> Below, please describe a set of hypotheses (both null and alternative) related to this data that can be tested using a t-test. [2 points]


### Data Analysis

> In the code chunk below, please carry out a t-test that will test the hypotheses listed above. Then, below the code chunk, summarize the results of this analysis. Make particular reference to relevant statistics, including t-value and p-value (statistical significance). [3 points]

```{r}

```



### Conclusions

> Below, interpret the results of this analysis (that is, describe what the results mean for your data). Please also discuss any practical implications of these results (that is, explain how people might wish to think or act differently based on these results). [1 points]



## Project 3, Part 3: Regression [8 points]

> For this part of the project, you will be carrying out a regression. Please recall that the purpose of regression is to describe the relationship between two (or more) variables!

### Hypotheses

> Below, please describe a set of hypotheses (both null and alternative) related to this data that can be tested using regression. [2 points]


### Data Analysis

> In the code chunk below, please carry out a regression that will test the hypotheses listed above. Then, below the code chunk, summarize the results of this analysis. Make particular reference to relevant statistics, including beta (coefficient), t-value and p-value (statistical significance). [4 points]

```{r}

```

### Conclusions

> Below, interpret the results of this analysis (that is, describe what the results mean for your data). Please also discuss any practical implications of these results (that is, explain how people might wish to think or act differently based on these results). [2 points]



# Submitting Project 4

After you've completed all parts of this assignment to your satisfaction, click on the `Knit` button in the toolbar at the top of this pane. When/if prompted, please indicate that you wish to knit to an HTML file. Knitting to PDF or Word are fancy tricks but take some more setting up, and that's beyond the scope of this class. 

After RStudio has finished knitting the file, it will bring it up in a special RStudio interface. You can use this interface to review the document and make sure that everything appears as you want. Then, however, you should navigate to the same folder where you have stored this `.Rmd` file, and you will find a `.html` file with the same name in that same folder. You can open that file to view this in your browser; more importantly, this is the file that you should submit to Canvas to complete this assignment.

I cannot accept any submission of your work besides the knit `.html` file! If you are having trouble knitting, please get in touch with me instead of submitting the `.Rmd` file and hoping it will work instead. It won't. I don't have your data, I won't see your output, and I can't grade your work without either of those.

Speaking of having your data, though, it would be nice to have access to all the work you've done in addition to the `.html` file. Please open GitHub desktop, navigate to your repository for this class, *commit* the changes that you've made in completing this project, and *push* those changes to GitHub. I will also ask you to do this if you need any help along the way.