---
title: "ICT_LIS_661_Project_2"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Welcome to Code Chunks!

Our last project `.Rmd` file introduced but didn't actually use code chunks, so it's worth touching on those again before we dive back into the project. 

Remember that R Markdown is a way for data scientists to share their code **and** write up their research. Regular Markdown features help data scientists format their regular writing, and then *code chunks* display—and run—code alongside writing and commentary.

Here's what a code chunk looks like:

```{r}
1 + 1
```

When the `.Rmd` document is knit to HTML, not only does the Markdown stuff get formatted, but all of these code chunks are run, so that the code itself **and** the results will appear in the final document. Pretty nifty!

That said, it's usually better to run the code before you knit the file—you know, to make sure the code works properly before you publish it. In that case, you can hit the green "play" button in the top right of the code chunk, and the code will run and display the results—not in the usual console, but in a mini-console attached to the code itself. Try it out on the code-chunk above. You'll need to run your own code to test it as you work with `.Rmd` documents in this class.

# Welcome to Project 2!

Before moving on, please make a copy of this file and rename it in a way that makes a clear distinction between the original file and the file you'll eventually submit.

> Under the headers below, I'll provide you with certain instructions, all of them formatted as blockquotes, like this paragraph is. Underneath each set of blockquoted instructions, you should write a (non-blockquoted) response to any questions I ask and fill out any code chunks as I instruct you. At the very end of this document, I'll provide instructions for *knitting* and submitting the `.Rmd` to Canvas.

## Project 2, Part 1: Your Dataset [8 points]

> For this project, you will need to identify a dataset with at least 100 observations and 5 variables. A dataset with at least 1,000 observations and 10 variables would be even better—but not necessary. It is fine for this to be a dataset that you have used previously in this class. This does not need to be a publicly available dataset, but please ensure that you can use the dataset legally and ethically. Store the data somewhere in your GitHub repository for this class.

> In the code chunk below, please load the dataset into this document. (Keep in mind that you can—and may need to—install and load packages as part of this or any other code chunk). [2 points]

```{r}
World_Risk_Index <- read_csv("C:/Users/Joey Bates/Desktop/School/UK/3rd Semester/ICT661 Intro to Data Science/Wk4/World Risk Index.csv")
View(World_Risk_Index)
```

> Now that you've loaded the dataset, please tell me some about it. Does it have a title? If not, what title would you give it? What reference or citation information (including a public URL, if applicable) can you provide about the dataset? Who created the dataset and when? How did they create it? [2 points]

The data set provided (World_Risk_Index) was derived from the website Kaggle. The World Risk Report is an annual technical report on global disaster risks and identifies the risk of an extreme natural event becoming a disaster for numerous countries worldwide.
Tyagi, M. (2022, September 7). World disaster risk dataset. Kaggle. Retrieved October 13, 2022, from https://www.kaggle.com/datasets/tr1gg3rtrash/global-disaster-risk-index-time-series-dataset 
According to the Kaggle website the originator of this risk index was Mrinal Tyagi, who finalized the assessment September 7th, 2022. The World Risk Index uses 27 aggregated, publicly available indicators to determine disaster risk for 181 countries worldwide. Conceptually, the index is composed of exposure to extreme natural hazards and the societal vulnerability of individual countries. Earthquakes, cyclones, floods, droughts, and climate-induced sea-level rise are considered in the exposure analysis. Societal vulnerability is divided into susceptibility to extreme natural events, lack of coping capacities, and lack of adaptive capacities. All index components are scaled to the value range from 0 to 100. The higher a country's index score on the World Risk Index, the higher its national disaster risk.

> What is your interest in this dataset? In general terms, what would you like to know about it? More specifically, what are some possible research questions that you could ask? [2 points]

My undergraduate degree is in Homeland Security, and I have spent substantial amount of my career in emergency management roles which has sparked my interest in predictive analysis in an emergency management index. I would also like to know if there are indicators within the data that predict disaster susceptibility which can be used by NGO organizations like US AID to allocate resources appropriately. The two Research Questions (RQs) that I would as are: 1) What top five countries are more susceptible and vulnerable to natural disasters? 2)  What regions of the world have a higher disaster exposure score?

> As needed, perform any data cleaning (including "tidying") on the text in the code chunk below. [2 points]

```{r}
World_Risk_Index %>% arrange(Year, Region)
```

## Project 2, Part 2: Descriptive Statistics [12 points]

> In the code chunk below, write code to determine the number of observations in the dataset. As is typical for R, there are a number of ways to do this—*how* you do so is less important than *that* you do so. [2 points]

```{r}
World_Risk_Index %>%
  group_by(Region) %>%
  tally()
```

> In the code chunk below, write code to list the variables included in the dataset. Then, below the code chunk, list and explain 5-10 of the most important quantitative variables. (The quantitative part will become important in the next step!) [3 points]

```{r}
str(World_Risk_Index)
```

The following quantitative variables are important to the World Risk Index study. 
1) World Risk Index (WRI): This variable illustrates the risk index that has been applied to each region listed, and quantitatively where it falls in relation to other countries around the world. 
2) Exposure: This variable depicts the quantifiable exposure score that each country has assigned to it as it relates to natural disasters. 
3) Vulnerability: This variable depicts the quantifiable Vulnerability score that each country has assigned to it as it relates to natural disasters. 
4) Susceptibility: This variable depicts the quantifiable Susceptibility score that each country has assigned to it as it relates to natural disasters.
5) Lack of Coping Capabilities: This variable communicates the quantifiable identifier that has been assigned to a country's ability to cope during a natural disaster.
6) Lack of Adaptive Capacities: This variable communicates the quantifiable identifier that has been assigned to a country's ability to adapt during a natural disaster.

> In the code chunk below, calculate descriptive statistics (including mean, median, variance, and standard deviation) for each of the variables you listed above. Then, below the code chunk, describe what those descriptive statistics tell you about those variables. [3 points]

```{r}
World_Risk_Index %>%
  group_by(Region) %>%
  summarize_at(vars(WRI, Exposure, Vulnerability, Susceptibility, `Lack of Coping Capabilities`, `Lack of Adaptive Capacities`, Year), list(~mean(.), ~median(.)))
```

> Consider further questions that you have about the data and how visualization could help you answer those questions. In the code chunk below, pick one or more of the variables in your dataset and visualize them. Then, below the code chunk, describe what you were trying to learn about the data, what kind of plot you chose, why that plot is important for what you were trying to learn, and what the plot showed about the data. [4 points]

```{r}
ggplot(data = WRI) + 
  geom_point(mapping = aes(x = Region, y = Exposure), color = "blue")
```
What you are trying to learn about the data? 
What kind of plot you chose?
Why that plot is important to what you are trying to learn? 
What did the plot show about the data? 

# Submitting Project 2

After you've completed all parts of this assignment to your satisfaction, click on the `Knit` button in the toolbar at the top of this pane. When/if prompted, please indicate that you wish to knit to an HTML file. Knitting to PDF or Word are fancy tricks but take some more setting up, and that's beyond the scope of this class. 

After RStudio has finished knitting the file, it will bring it up in a special RStudio interface. You can use this interface to review the document and make sure that everything appears as you want. Then, however, you should navigate to the same folder where you have stored this `.Rmd` file, and you will find a `.html` file with the same name in that same folder. You can open that file to view this in your browser; more importantly, this is the file that you should submit to Canvas to complete this assignment.

I cannot accept any submission of your work besides the knit `.html` file! If you are having trouble knitting, please get in touch with me instead of submitting the `.Rmd` file and hoping it will work instead. It won't. I don't have your data, I won't see your output, and I can't grade your work without either of those.

Speaking of having your data, though, it would be nice to have access to all the work you've done in addition to the `.html` file. Please open GitHub desktop, navigate to your repository for this class, *commit* the changes that you've made in completing this project, and *push* those changes to GitHub. I will also ask you to do this if you need any help along the way.